---
title: "00_Data_Check_Visual"
output: html_document
---

```{r setup, warning=FALSE, message=FALSE}
library(tidyverse)
library(haven)
library(forcats)
library(ggplot2)
library(rlang)
library(descr)
library(mice)
library(ggridges)
```

```{r}
load("~/Hertie School/40_Masters_Thesis/Empirical/Raw_Data/consumer_level_metrics_all_respondents_ger.RData")


load("~/Hertie School/40_Masters_Thesis/Empirical/Raw_Data/meof_ger_df.RData")
```

# Consumer Metrics Data Check

```{r}
cm <- ger_consumer_level_metrics |> 
  select(c(personid, total_visits_news_sites, total_visits_overall)) |> 
  mutate(news_proportion = total_visits_news_sites / total_visits_overall)

cm <- cm |> select(personid, news_proportion)
```

```{r}
cm |> ggplot(aes(news_proportion)) +
  geom_boxplot()
```

**Selecting the respondents who will be accidentally removed but later added back in**

These people have no news visits.

# Survey Data Check

## German Survey Data

\*Might keep for analysis, not for ML

(**wave**)

1.  wave\* **1**

2.  personid **1**

3.  gender (**1**-8)

4.  birthmonth (**1**)

5.  birthyear (**1**)

6.  age (**5**) - *We will use wave 5 because that's the age of when they voted*

7.  {voceduc (1,**2**) : ml_degreestatus} - *We will use wave 2 data here because its the most recent information*

8.  {relationship (1,**2**): ml_relationship} - *We will use wave 2 data here because its the most recent information*

9.  {maritalstatus (**1**): ml_married}

10. {employment (1,**2**): ml_employ} - *We will use wave 2 data here because its the most recent information*

11. hhincome (**2**)\*

12. postcode \*

13. {polinterest (1,**4**,6): ml_polinterest} - *We will use wave 4 data here because its the most recent information*

14. secondvote (**5**)

### **Selecting Columns**

**Wave 1 Variables: Respondent Details**

```{r}
baseline <- meof_ger_df |> 
  select(wave, personid, gender, birthmonth, birthyear, maritalstatus, postcode) |> 
  filter(wave == 1)

baseline <- baseline |> 
  mutate(
    fgender = as_factor(gender),
    fmaritalstatus = as_factor(maritalstatus)
  )

```

```{r}
explore <- function(data, list_of_columns) {
  plots <- list()  # Initialize an empty list to store the plots
  
  # Loop through each item in the list of columns
  for (item in list_of_columns) {
    
    # Check if the column is a factor or character variable (categorical)
    if (is.factor(data[[item]]) | is.character(data[[item]])) {
      # Convert to factor and explicitly include NAs as a separate level
      data[[item]] <- factor(data[[item]], exclude = NULL)
      
      img <- ggplot(data, aes(x = !!sym(item))) + 
        geom_bar(fill = "steelblue", color = "black") +  # Normal bars for non-NA values
        # Add a red bar for NA values
        geom_bar(data = data %>% filter(is.na(!!sym(item))), 
                 aes(x = "NA"), fill = "red", color = "black") +  
        labs(
          title = paste(item, "Distribution"),
          x = item,
          y = "Count",
          caption = "Source: meof_ger_df"
        ) +
        theme_minimal() +
        theme(axis.text.x = element_text(angle = 45, hjust = 1))
        
    } else {
      # For numeric variables: Handle NA values separately
      # Replace NA values with a placeholder (e.g., "Missing")
      data[[item]] <- ifelse(is.na(data[[item]]), "Missing", as.character(data[[item]]))
      
      img <- ggplot(data, aes(x = !!sym(item))) + 
        geom_bar(fill = "steelblue", color = "black") +  # Normal bars for non-NA values
        # Add a red bar for Missing values (treated as categorical)
        geom_bar(data = data %>% filter(!!sym(item) == "Missing"), 
                 aes(x = !!sym(item)), fill = "red", color = "black") +  
        labs(
          title = paste(item, "Distribution"),
          x = item,
          y = "Count",
          caption = "Source: meof_ger_df"
        ) +
        theme_minimal() +
        theme(axis.text.x = element_text(angle = 45, hjust = 1))
    }
    
    # Store each plot in the list
    plots[[item]] <- img
  }
  
  return(plots)  # Return the list of plots
}

list_of_columns <- c("fgender", "fmaritalstatus")  
plots <- explore(baseline, list_of_columns)

# To display the plots, you can either print them one by one:
print(plots[["fgender"]])
print(plots[["fmaritalstatus"]])

```

**Wave 2 Variables: Respondent Details (Most Recent)**

```{r}
w2items <- meof_ger_df |>
  select(wave, personid, voceduc, relationship, employment) |>
  filter(wave == 2)

w2items <- w2items |> 
  mutate(
    fvoceduc = as_factor(voceduc),
    frelationship = as_factor(relationship),
    femployment = as_factor(employment)
  )

```

```{r}
list_of_columns <- c("fvoceduc", "frelationship", "femployment")  
plots <- explore(w2items, list_of_columns)

# To display the plots, you can either print them one by one:
print(plots[["fvoceduc"]])
print(plots[["frelationship"]])
print(plots[["femployment"]])

```

**Wave 4 Variable: Interest in Politics**

```{r}
polint <- meof_ger_df |>
  select(wave, personid, polinterest) |>
  filter(wave == 4)
```

```{r}
table(polint$polinterest)
```

```{r}
polint$polinterest <- na_if(polint$polinterest, 977)
```

```{r}
polint |> 
  mutate(polinterest = as_factor(polinterest)) |>
  ggplot(aes(x = polinterest)) + 
  geom_bar(fill = "steelblue", color = "black") + 
  labs(
    title = "Interest in Politics",
    x = "Interest",
    y = "Count",
    caption = "Source: meof_ger_df"
  ) +
  theme_minimal() + 
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1), 
    plot.title = element_text(hjust = 0.5) 
  )


```

**Wave 5 Variable: Voting Behavior**

```{r}
voting <- meof_ger_df |>
  filter(wave == 5, !is.na(voted_2017)) |>
  select(personid, age, secondvote)
```

```{r}
table(voting$secondvote)
```

```{r}
voting$secondvote <- na_if(voting$secondvote, 977)
voting$secondvote <- na_if(voting$secondvote, 7)
```

```{r}
voting |>
  filter(secondvote != 977 & secondvote != 7 & !is.na(secondvote)) |>
  mutate(secondvote = as_factor(secondvote)) |>
  ggplot(aes(x = secondvote)) + 
  geom_bar(fill = "steelblue", color = "black") + 
  labs(
    title = "Vote in Federal Election",
    x = "Party",
    y = "Count",
    caption = "Source: meof_ger_df"
  ) +
  theme_minimal() + 
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1), 
    plot.title = element_text(hjust = 0.5) 
  )
```

```{r}
voting <- voting |>
  mutate(
    adjustedvote = case_when(
      secondvote == 5 ~ -3,
      secondvote == 4 ~ -2,
      secondvote == 2 ~ -1,
      secondvote %in% c(7, 997) | is.na(secondvote) ~ 0,
      secondvote == 3 ~ 1,
      secondvote == 1 ~ 2,
      secondvote == 6 ~ 3,
      TRUE ~ 0
    ),
    adjustedvotelr = case_when(
      secondvote == 5 ~ -1,
      secondvote == 4 ~ -1,
      secondvote == 2 ~ -1,
      secondvote %in% c(7, 997) | is.na(secondvote) ~ 0,
      secondvote == 3 ~ 1,
      secondvote == 1 ~ 1,
      secondvote == 6 ~ 1,
      TRUE ~ 0
  ))

```

```{r}
voting |>
  ggplot(aes(x = factor(adjustedvote))) +  # Convert to factor to ensure all labels appear
  geom_bar(fill = "steelblue", color = "black") + 
  labs(
    title = "Vote in Federal Election (Readjusted)",
    subtitle = "Larger Negative Numbers = 'More Left Wing' | Larger Positive Numbers = 'More Right Wing'",
    x = "Party",
    y = "Count",
    caption = "Source: meof_ger_df"
  ) +
  theme_minimal() + 
  theme(
    plot.title = element_text(hjust = 0.5),
    axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)  # Rotate x labels for better readability
  )

```

```{r}
voting |>
  ggplot(aes(x = factor(adjustedvotelr))) +  # Convert to factor to ensure all labels appear
  geom_bar(fill = "steelblue", color = "black") + 
  labs(
    title = "Vote in Federal Election (Readjusted)",
    subtitle = "Larger Negative Numbers = 'More Left Wing' | Larger Positive Numbers = 'More Right Wing'",
    x = "Party",
    y = "Count",
    caption = "Source: meof_ger_df"
  ) +
  theme_minimal() + 
  theme(
    plot.title = element_text(hjust = 0.5),
    axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)  # Rotate x labels for better readability
  )
```

**Wave 2 Variable: Income (Most Recent)**

```{r}
income <- meof_ger_df |>
  select(wave, personid, hhincome) |>
  filter(wave == 2) |>
  select(!wave)
```

```{r}

levels(income$hhincome)
table(income$hhincome)
```

```{r}
income <- income |> mutate(
  hhincome = as.numeric(as.character(hhincome)),  # Ensure pincome is numeric
  adjustedincome = case_when(
    hhincome == 13 ~ NA,
    is.na(hhincome) ~ NA,
    TRUE ~ hhincome
  )
)

income |>
  ggplot(aes(x = factor(adjustedincome))) +  # Convert to factor for proper labeling
  geom_bar(fill = "darkgreen", color = "black") + 
  labs(
    title = "Household Income",
    x = "Income",
    y = "Count",
    caption = "Source: meof_ger_df"
  ) +
  theme_minimal() + 
  theme(
    plot.title = element_text(hjust = 0.5),
    axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)  # Rotate labels
  )


```

### Rejoining the Tables

```{r}

survey <- left_join(voting, baseline, by = "personid")

survey <- left_join(survey, cm , by = "personid")

survey <- left_join(survey, w2items, by = "personid")

survey <- left_join(survey, polint , by = "personid")

survey <- left_join(survey, income, by = "personid")

```

## Handling NA Values

Note: This is from 03_Survey_Tracking_Merging output.

```{r}

master <- read.csv("~/Hertie School/40_Masters_Thesis/Empirical/Processed_Data/31_merged_wide.csv")

```

```{r}
#survey <- survey |> filter(personid %in% master$personid | personid %in% nonews$personid)

```

```{r}
survey <- survey |> 
  select(-wave.x, -wave.y) |> 
  mutate(news_proportion = ifelse(is.na(news_proportion), 0, news_proportion))

# Count NAs per column
na_counts <- data.frame(sapply(survey, function(x) sum(is.na(x))))

# View the result
na_counts


```

```{r}
# List of columns to plot
list_of_columns <- c("secondvote", "voceduc", "relationship", "employment", 
                     "fvoceduc", "frelationship", "femployment", 
                     "polinterest", "hhincome", "adjustedincome")

# Generate the plots
plots <- explore(survey, list_of_columns)

print(plots[["secondvote"]])
print(plots[["voceduc"]])
print(plots[["relationship"]])
print(plots[["employment"]])
print(plots[["polinterest"]])
print(plots[["hhincome"]])
print(plots[["adjustedincome"]])

```

```{r, echo = T, results = 'hide'}
survey$secondvote[is.na(survey$secondvote)] <- 0

library(Hmisc)

# Impute missing values using the median for all columns in the dataset
imputed <- as.data.frame(lapply(survey, function(x) impute(x, fun = median)))

```

```{r}
# List of columns to plot
list_of_columns <- c("secondvote", "voceduc", "relationship", "employment", 
                     "fvoceduc", "frelationship", "femployment", 
                     "polinterest", "hhincome", "adjustedincome")

# Generate the plots
plots <- explore(imputed, list_of_columns)

print(plots[["secondvote"]])
print(plots[["voceduc"]])
print(plots[["relationship"]])
print(plots[["employment"]])
print(plots[["polinterest"]])
print(plots[["hhincome"]])
print(plots[["adjustedincome"]])
```

```{r}
# Count NAs per column
na_post <- data.frame(sapply(imputed, function(x) sum(is.na(x))))

# View the result
na_post
```

# Visualizing Relationships

```{r}
imputed |> 
  mutate(secondvote = as_factor(secondvote)) |>
  filter(secondvote != "Andere Partei" & secondvote != "977") |>
  ggplot(aes(x = adjustedincome, y = secondvote)) +
  geom_density_ridges() +
  theme_ridges() + 
  theme(legend.position = "none")




```

```{r}
imputed |> 
  mutate(secondvote = as_factor(secondvote)) |> 
  filter(secondvote != "Andere Partei" & secondvote != "977") |>
  ggplot(aes(x = age, y = secondvote)) +
  geom_density_ridges() +
  theme_ridges() + 
  theme(legend.position = "none")
```

```{r}
imputed |> 
  mutate(secondvote = as_factor(secondvote)) |> 
  filter(secondvote != "Andere Partei" & secondvote != "977") |>
  ggplot(aes(x = birthyear, y = secondvote)) +
  geom_density_ridges() +
  theme_ridges() + 
  theme(legend.position = "none")
```

```{r}
imputed |> 
  mutate(
    secondvote = as_factor(secondvote),
    polinterest = as.factor(polinterest)
  ) |>  # Ensure polinterest is a factor
  filter(secondvote != "Andere Partei" & secondvote != "977") |>  # Filter out specific secondvote values
  ggplot(aes(x = secondvote, fill = secondvote)) +  # Use secondvote for x-axis and fill by secondvote
  geom_bar(aes(y = after_stat(count)), position = "dodge") +  # Position bars side by side
  facet_wrap(~polinterest) +  # Create facets for each level of polinterest
  scale_fill_manual(
    values = c(
      "AfD" = "lightblue", 
      "Die Linke" = "purple", 
      "FDP" = "yellow", 
      "SPD" = "red", 
      "CDU/CSU" = "blue", 
      "B?ndnis 90/Die Gr?nen" = "green",
      "Other" = "gray"  # Color for all other categories
    )
  ) +
  theme_minimal() +  # Use a minimal theme for clarity
  theme(
    legend.position = "none",  # Remove the legend
    axis.text.x = element_text(angle = 45, hjust = 1)  # Rotate x-axis labels for better readability
  ) +
  labs(x = "Second Vote", y = "Count")  # Add axis labels




```

```{r}
imputed |> 
  mutate(
    secondvote = as_factor(secondvote),
    polinterest = as_factor(voceduc)
  ) |>  # Ensure polinterest is a factor
  filter(secondvote != "Andere Partei" & secondvote != "977") |>  # Filter out specific secondvote values
  ggplot(aes(x = secondvote, fill = secondvote)) +  # Use secondvote for x-axis and fill by secondvote
  geom_bar(aes(y = after_stat(count)), position = "dodge") +  # Position bars side by side
  facet_wrap(~voceduc) +  # Create facets for each level of polinterest
  scale_fill_manual(
    values = c(
      "AfD" = "lightblue", 
      "Die Linke" = "purple", 
      "FDP" = "yellow", 
      "SPD" = "red", 
      "CDU/CSU" = "blue", 
      "B?ndnis 90/Die Gr?nen" = "green",
      "Other" = "gray"  # Color for all other categories
    )
  ) +
  theme_minimal() +  # Use a minimal theme for clarity
  theme(
    legend.position = "none",  # Remove the legend
    axis.text.x = element_text(angle = 45, hjust = 1)  # Rotate x-axis labels for better readability
  ) +
  labs(x = "Second Vote", y = "Count")  # Add axis labels
```

```{r}
imputed |> 
  ggplot(aes(x = factor(secondvote), y = log(news_proportion))) +
  geom_boxplot()



```

# Write to CSV

```{r}
imputed |> write.csv("~/Hertie School/40_Masters_Thesis/Empirical/Processed_Data/00_labeled_survey.csv", row.names = FALSE)
```
