---
title: "Data_Columns"
author: "Ray Hossain"
output: html_document
---

```{r}
library(tidyverse)
library(haven)
library(forcats)
```

```{r}
load("~/Hertie School/40_Masters_Thesis/Empirical/Raw_Data/consumer_level_metrics_all_respondents_ger.RData")


load("~/Hertie School/40_Masters_Thesis/Empirical/Raw_Data/meof_ger_df.RData")
```

# Data Objectives (Feature Selection)

## Consumer Data

-   personid

-   total_visits_overall

-   total_visits_news_sites

-   {CREATE: news_proportion= total visits news sites / total visits overall}

```{r}
ger_consumer_level_metrics |> colnames() |> data.frame()
```

```{r, ignore = True}
cm <- ger_consumer_level_metrics |> 
  select(c("personid", "total_visits_news_sites","total_visits_overall")) |> 
  mutate(news_proportion = total_visits_news_sites / total_visits_overall)

cm <- cm |> select(personid, news_proportion)

#cm |> write.csv("10_consumer_metrics.csv")

```

## German Tracking Data

Keep all. For more details, check Cleaning.Rmd.

```{r}
#tracking_df_ger_news |> colnames() |> as.data.frame()
```

## German Survey Data

\*Might keep for analysis, not for ML

(**wave**)

1.  wave\* **1**

2.  personid **1**

3.  gender (**1**-8)

4.  birthmonth (**1**)

5.  birthyear (**1**)

6.  age (**5**) - *We will use wave 5 because that's the age of when they voted*

7.  {voceduc (1,**2**) : ml_degreestatus} - *We will use wave 2 data here because its the most recent information*

    -   1,2,3,4,6 -\> 0 No degree

    -   5 -\> 1 Degree

8.  {relationship (1,**2**): ml_relationship} - *We will use wave 2 data here because its the most recent information*

    -   3,4,5 -\> 0 No relationship

    -   1,2 -\> 1 In a relationship

9.  {maritalstatus (**1**): ml_married}

    -   2 -\> 1 Married

    -   1,3,4,5,6,7,8 -\> 0 Not Married

10. {employment (1,**2**): ml_employ} - *We will use wave 2 data here because its the most recent information*

    -   1 -\> 1 employed

    -   all others -\> 0 unemployed

11. pincome (**6**)\*

12. postcode \*

13. {polinterest (1,**4**,6): ml_polinterest} - *We will use wave 4 data here because its the most recent information*

    -   1,2, 3, 6 -\> 0 Low in politics

        -   We are setting everything below outright interest as low interest

    -   4,5 -\> 1 high interest in politics

14. {voted_2017 (**5**): ml_vote}

    -   1 -\> 1 Voted

    -   2,3,4 -\> 0 Did not vote

15. firstvote (**5**)

16. secondvote (**5**)

```{r}
meof_ger_df |> colnames() |> as.data.frame()
```

```{r}
voters <- meof_ger_df |> 
  select(wave, voted_2017, secondvote) |>
  filter(wave == 5, voted_2017 == 1)
```

**Checking whether I want work status or employment as an indicator**

```{r}
e1 <- meof_ger_df |> 
  select(workstatus, wave) |> 
  filter(wave %in% c(1, 2)) |>  # Filter for wave 1 or 2
  count(workstatus)

# Create a bar plot
barplot(e1$n, names.arg = e1$workstatus, xlab = "Work Status", ylab = "Count", main = "Work Status Distribution")
```

```{r}
e2 <- meof_ger_df |> 
  select(employment, wave) |> 
  filter(wave %in% c(1, 2)) |>  # Filter for wave 1 or 2
  count(employment) 

# Create a bar plot
barplot(e2$n, names.arg = e2$employment, xlab = "Employment", ylab = "Count", main = "Work Status Distribution")
```

Choosing employment because it has more values.

### **Selecting Columns**

**Wave 1 Variables: Respondent Details**

```{r}
baseline <- meof_ger_df |> 
  select(wave, personid, gender, birthmonth, birthyear, maritalstatus, postcode) |> 
  filter(wave == 1)

```

```{r}
baseline |> distinct(gender)
baseline |> distinct(maritalstatus)
```

```{r}
b2 <- baseline |> select(!wave) |>
  mutate(
    ml_married = factor(      
      case_when(
        zap_labels(maritalstatus) == 2 ~ 1,
        zap_labels(maritalstatus) != 2 ~ 0
      ),
      levels = c(0, 1)),
    ml_gender_female = factor(      
      case_when(
        zap_labels(gender) == 2 ~ 1,
        zap_labels(gender) != 2 ~ 0
      ),
      levels = c(0, 1)      
    )
  ) 

b3 <- b2 |> select(personid, ml_gender_female, ml_married)
  
```

```{r}
library(ggplot2)

ggplot(b2, aes(x = ml_married)) +
  geom_bar(fill = "lightblue") +
  labs(title = "Distribution of Marital Status",
       x = "Marital Status",
       y = "Frequency") +
  theme_minimal()
```

**Wave 2 Variables: Respondent Details (Most Recent)**

```{r}
w2items <- meof_ger_df |>
  select(wave, personid, voceduc, relationship, employment) |>
  filter(wave == 2)
```

```{r}
w2items |> distinct(voceduc)
w2items |> distinct(relationship)
w2items |> distinct(employment)
```

Recoding the variables

```{r}

w2 <- w2items |> select(!wave) |>
  mutate(
    # Create ml_degreestatus as a factor with numeric levels
    ml_degreestatus = factor(
      case_when(
        zap_labels(voceduc) == 5 ~ 1,
        zap_labels(voceduc) != 5 ~ 0
      ),
      levels = c(0, 1) 
    ),
    
    # Create ml_relationship as a factor with numeric levels
    ml_relationship = factor(
      case_when(
        zap_labels(relationship) %in% c(1, 2) ~ 1,  # In a relationship
        zap_labels(relationship) >= 3 ~ 0            # Not in a relationship
      ),
      levels = c(0, 1)  
    ),
    
    # Create ml_employ as a factor with numeric levels
    ml_employ = factor(
      case_when(
        zap_labels(employment) == 1 ~ 1,  # Employed
        zap_labels(employment) != 1 ~ 0   # Not employed
      ),
      levels = c(0, 1)  
  )) 

mlw2 <- data.frame(
  personid = w2$personid,
  ml_relationship = w2$ml_relationship,
  ml_employ = w2$ml_employ,
  ml_degreestatus = w2$ml_degreestatus
)

```

```{r}
# Plot ml_degreestatus
p1 <- ggplot(mlw2, aes(x = ml_degreestatus)) +
  geom_bar(fill = "lightblue") +
  labs(title = "Distribution of Degree",
       x = "Degree Status",
       y = "Frequency") +
  theme_minimal()

# Plot ml_relationship
p2 <- ggplot(mlw2, aes(x = ml_relationship)) +
  geom_bar(fill = "lightgreen") +
  labs(title = "Distribution of Relationship",
       x = "Relationship Status",
       y = "Frequency")+
  theme_minimal()

# Plot ml_employ
p3 <- ggplot(mlw2, aes(x = ml_employ)) +
  geom_bar(fill = "lightcoral") +
  labs(title = "Distribution of Employment",
       x = "Employment Status",
       y = "Frequency") +
  theme_minimal()

# Display all plots
library(patchwork)  # For arranging plots
p1 + p2 + p3
```

**Wave 4 Variable: Interest in Politics**

```{r}
polint <- meof_ger_df |>
  select(wave, personid, polinterest) |>
  filter(wave == 4)
```

```{r}

mlw4 <- polint |> select(!wave) |>
  mutate(
    ml_political_interest = factor(
      case_when(
        !zap_labels(polinterest) %in% c(4, 5) ~ 0,
        zap_labels(polinterest) %in% c(4, 5) ~ 1
      ),
      levels = c(0, 1)  # Define the levels explicitly
    )
  ) |> select(!polinterest) #Get rid of the non-ml
```

```{r}
ggplot(mlw4, aes(x = ml_political_interest)) +
  geom_bar(fill = "lightblue") +
  labs(title = "Distribution of Interest",
       x = "Political Interest",
       y = "Frequency") +
  theme_minimal()
```

**Wave 5 Variable: Voting Behavior**

```{r}
#voting <- meof_ger_df |>
#  select(wave, personid, age, secondvote) |>
#  filter(wave == 5) |>
#  select(!wave)
```

```{r}
voting <- meof_ger_df |>
  filter(wave == 5, !is.na(voted_2017)) |>
  select(personid, age, secondvote) 
```

```{r}
voting |> distinct(secondvote) 
```

Modifying so that it is one-hot encoded

```{r}
ml_voting <- voting |>
  mutate(
    vote_cdu = ifelse(secondvote == 1 & !is.na(secondvote), 1, 0),
    vote_spd = ifelse(secondvote == 2 & !is.na(secondvote), 1, 0),
    vote_fdp = ifelse(secondvote == 3 & !is.na(secondvote), 1, 0),
    vote_green = ifelse(secondvote == 4 & !is.na(secondvote), 1, 0),
    vote_left = ifelse(secondvote == 5 & !is.na(secondvote), 1, 0),
    vote_afd = ifelse(secondvote == 6 & !is.na(secondvote), 1, 0),
    vote_na_other = ifelse(secondvote %in% c(7, 997) | is.na(secondvote), 1, 0)
  )
```

**Wave 6 Variable: Income (Most Recent)**

```{r}
income <- meof_ger_df |>
  select(wave, personid, pincome) |>
  filter(wave == 6) |>
  select(!wave)
```

### Rejoining the Tables

```{r}

survey <- left_join(ml_voting, b3, by = "personid")

survey <- left_join(survey, cm, by = "personid")

survey <- left_join(survey, mlw2, by = "personid")

survey <- left_join(survey, mlw4, by = "personid")

#survey <- left_join(survey, income, by = "personid")

```

```{r}
#sapply(survey, class)
```

Change the NAs to 7, change the second vote column to have an "other" category.

```{r}
survey <- survey |>
  mutate(across(-secondvote, ~ replace(., is.na(.), 0)))

survey <- survey %>%
  mutate(secondvote = case_when(
    secondvote == 977 | secondvote == 7 | is.na(secondvote) ~ 7,
    TRUE ~ secondvote
  ))
```

```{r}
library(ggplot2)

ggplot(survey, aes(x = secondvote)) +
  geom_bar(fill = "lightblue") +
  labs(title = "Distribution of Vote",
       x = "Vote",
       y = "Frequency") +
  theme_minimal()
```

```{r}
survey |> write.csv("~/Hertie School/40_Masters_Thesis/Empirical/Processed_Data/11_survey_filtered.csv")

```
